Trends in Toronto Homeless Deaths and Their Underlying Causes

### 2024-09-24 paper/paper.qmd
Add files via upload

---
title: "Marriage Licence Statistics"
subtitle: ""
author: 
  Ariel Xing
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

>>>>

---
title: "Trends in Toronto Homeless Deaths and Their Underlying Causes"
subtitle: ""
author: 
  Ariel Xing
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Toronto consistently faces a significant population of individuals experiencing homelessness. This study examines the pattern of mortality among this population and the underlying causes of these deaths. The data form Open Data Toronto suggests that three main causes of deaths are seasons, covid-19 and drugs(?). By understanding the factors contributing to these deaths, the government can enhance its capacity to assist and protect the lives of the homeless, safeguard their rights and interests, and promoting social stability."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```

@@

```
